---
title: "CS6313.002 Statistical Project 1"
author: Ruolan Zeng(rxz171630), Vineet Vilas Amonkar(vva180000), Aakash Kamlesh Punjabi(
  akp170430)
date: "October 24, 2018"
output: html_document
---
## Alternate method

Loading the token data:


```{r}
tokenData <- read.delim("networkstorjTX.txt", header = FALSE, sep = " ")
tokenFrame<- as.data.frame(tokenData)
colnames(tokenFrame)<-c('fromNode','toNode','unixTime','totalAmount')
head(tokenFrame)
```

Removing Outliers from the token data:


```{r}
TotalSupply <- 424999998
Decimals <- 10^8
OutlierValue <- TotalSupply*Decimals
WithoutOutlierdata <- tokenFrame[ which(tokenFrame$totalAmount < OutlierValue),]
head(WithoutOutlierdata)


```

Summary of the token data without outlier:

```{r}
summary(WithoutOutlierdata$totalAmount)

```

Max amount of the token data without outlier:

```{r}
max(WithoutOutlierdata$totalAmount)
```

First step: Ensure that the Storj token data is within the time frame of the Price Data

Following is the date interval of the price data:

Start Date: 07/02/2017
End Date: 07/15/2018

Lets check the date range for the token data

First convert the Unix time of the token data to Date format

```{r}
newwithoutoutlierdata <- WithoutOutlierdata
newwithoutoutlierdata$unixTime <- as.Date(as.POSIXct(WithoutOutlierdata$unixTime,origin="1970-01-01",tz="GMT"))
class(newwithoutoutlierdata$unixTime)


```

loading the price data :
```{r}
priceData <- read.delim("storj", header = TRUE, sep = "\t")
head(priceData)
priceData$Date <- as.Date(priceData$Date, "%m/%d/%Y")
head(priceData$Date)
```
add the price return to the dataframe:

```{r}

priceData$Open[1]
(priceData$Open[2]-priceData$Open[1])/priceData$Open[1]


```
create the price return column:
```{r}
return <- numeric(nrow(priceData))
return[1] <- priceData$Open[1]
for (i in 2:nrow(priceData)) {
  return[i] <- (priceData$Open[i]-priceData$Open[i-1])/priceData$Open[i-1]
}
return[2]
return
```
adding the price return column to the pricedata dataframe
```{r}
priceData$return <- return
priceData$return[2]
colnames(newwithoutoutlierdata)<-c('fromNode','toNode','Date','totalAmount')
newwithoutoutlierdata$Date[4]
```
merge both the dataframes according to dates
```{r}
newdataset <- merge(newwithoutoutlierdata,priceData,by = "Date")

```
